### 2022-12-06 README.Rmd
Minor cleanup
README.Rmd and more

---
output: github_document:
  html_preview: false
---

@@

## installation

The simplest way to install the package is to install the remotes package and run
```{r install, eval=FALSE}
#install.packages("devtools")
devtools::install_github("eirikmn/bremla")
```

>>>>

---
output: github_document
---

@@

## Installation

The simplest way to install the package is to install the remotes package and run
```{r install, eval=FALSE}
#install.packages("remotes")
remotes::install_github("eirikmn/bremla")
```

### 2022-12-06 inst/reproduce_results/results.Rmd
Minor cleanup
README.Rmd and more

 reference=res$original.chron$age[1+1:n]
 reftie = reference[res$tie_points$locations_indexes]
ggdtie = data.frame(mean=synchronization$params$mean-reftie,
                    upper=synchronization$params$mean+1.96*synchronization$params$sd-reftie,
                    lower=synchronization$params$mean-1.96*synchronization$params$sd-reftie,
                    locations = res$data$depth[synchronization$locations])
ggp2 = ggplot(data=ggd2,aes(x=depth)) + theme_bw()+
  geom_ribbon(aes(ymin=lower,ymax=upper),color="red",fill="red",alpha=0.3)+
  geom_line(aes(y=mean),color="blue") +
  geom_linerange(data=ggdtie,aes(x=locations,ymin=lower,ymax=upper),color="magenta")+
  xlab("Depth (m)") + ylab("Deviation from simulated reference (years)")+
  ggtitle("(b) Simulated chronologies")
library(gridExtra)
ggsave("fitdiffsim-5500x4000.eps", device=cairo_ps,width=5500,height=4000,units="px",dpi=500,limitsize=FALSE,arrangeGrob(ggp,ggp2))
str = ""
for(i in 1:length(res$fitting$inla$fit$summary.fixed$mean)){
  str=paste0(str," & & ",format(res$fitting$inla$fit$summary.fixed$mean[i],digits=7,scientific=FALSE), " & (",
             format(res$fitting$inla$fit$summary.fixed$`0.025quant`[i],digits=7,scientific=FALSE),", ",
             format(res$fitting$inla$fit$summary.fixed$`0.975quant`[i],digits=7,scientific=FALSE),") \\\\ \n")
}
cat(str)  
```

>>>>

 reference=res$original.chron$age[1+1:n]
 reftie = reference[res$tie_points$locations_indexes]
ggdtie = data.frame(mean=synchronization$params$mean-reftie,
                    upper=synchronization$params$mean+1.96*synchronization$params$sd-reftie,
                    lower=synchronization$params$mean-1.96*synchronization$params$sd-reftie,
                    locations = res$data$depth[synchronization$locations])
ggp2 = ggplot(data=ggd2,aes(x=depth)) + theme_bw()+
  geom_ribbon(aes(ymin=lower,ymax=upper),color="red",fill="red",alpha=0.3)+
  geom_line(aes(y=mean),color="blue") +
  geom_linerange(data=ggdtie,aes(x=locations,ymin=lower,ymax=upper),color="magenta")+
  xlab("Depth (m)") + ylab("Deviation from simulated reference (years)")+
  ggtitle("(b) Simulated chronologies")
library(gridExtra)
# ggsave("fitdiffsim-5500x4000.eps", device=cairo_ps,width=5500,height=4000,units="px",dpi=500,limitsize=FALSE,arrangeGrob(ggp,ggp2))
str = ""
for(i in 1:length(res$fitting$inla$fit$summary.fixed$mean)){
  str=paste0(str," & & ",format(res$fitting$inla$fit$summary.fixed$mean[i],digits=7,scientific=FALSE), " & (",
             format(res$fitting$inla$fit$summary.fixed$`0.025quant`[i],digits=7,scientific=FALSE),", ",
             format(res$fitting$inla$fit$summary.fixed$`0.975quant`[i],digits=7,scientific=FALSE),") \\\\ \n")
}
cat(str)  
```
